Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{The ideas discussed here first appeared as a DCSS project conference talk and were subsequently fleshed out in paper due to serendipitous encounters fostered by twitter.}

### 2016-02-28 has2016.tex
HAS 2016 camera ready
With Panos’ new UCL affiliation

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{This work has been supported in part by the European Commission through project NIFTy (ISEC 2012 Action Grants HOME/2012/ISEC/INT/4000003892). The ideas discussed appeared first as a talk at the Digital Citizenship and Surveillance Society project conference in Cardiff in June 2015. They were subsequently refined into this paper partly via serendipitous encounters enabled by the social medium of Twitter.}}
\subtitle{Policy lessons for Government after the Snowden leaks}

\author{Theo Tryfonas\inst{1} \and Michael Carter\inst{2} \and Tom Crick\inst{3} \and Panagiotis Andriotis\inst{1}}
\institute{Crypto Group, University of Bristol, UK\\
\email {\{t.tryfonas,p.andriotis\}@bristol.ac.uk}
\and
Surveillance Studies Centre, Queen's University, Canada\\
\email{michael.carter@queensu.ca} 
\and
Dept. of Computing, Cardiff Metropolitan University, UK\\
\email{tcrick@cardiffmet.ac.uk}}

>>>>

\title{Mass surveillance in cyberspace and the lost art of keeping a secret\thanks{This work has been supported in part by the European Commission through project NIFTy (ISEC 2012 Action Grants HOME/2012/ISEC/INT/4000003892). The ideas discussed appeared first as a talk at the Digital Citizenship and Surveillance Society conference in Cardiff in June 2015. They were subsequently refined into this paper partly via serendipitous encounters enabled by the social medium of Twitter.}}
\subtitle{Policy lessons for Government after the Snowden leaks}

\author{Theo Tryfonas\inst{1} \and Michael Carter\inst{2} \and Tom Crick\inst{3} \and Panagiotis Andriotis\inst{4}}
\institute{Crypto Group, University of Bristol, UK\\
\email {theo.tryfonas@bristol.ac.uk}
\and
Surveillance Studies Centre, Queen's University, Canada\\
\email{michael.carter@queensu.ca} 
\and
Dept. of Computing, Cardiff Metropolitan University, UK\\
\email{tcrick@cardiffmet.ac.uk}
\and
The Information Security Group, University College London, UK\\
\email{mr.panagiotis.andriotis@ieee.org}}
